% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\usepackage{hyperref}
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{24pt} % allow room for 2-line header
\setlength{\headsep}{24pt}  % space between header and text
\setlength{\headheight}{24pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
\rhead{ {\it Tamim}\\{\it p. \thepage} } % put text in header (right side)
\cfoot{}                                     % the foot is empty
\topmargin=-0.5in % start text higher on the page

\begin{document}
\thispagestyle{empty} % this page has no header  
\name{MD Iftakharul Islam\\[12pt]}% the \\[12pt] adds a blank line after name

\address{
  Website: \url{https://tamimcse.github.io/}\\
  Email: mislam4@kent.edu
  }      
                                      
\address{
Kent, Ohio, USA \\
Phone: 330-389-3188
  }
\begin{resume}

\section{\centerline{EDUCATION}} 
\vspace{2pt} 
{\sl PhD}, Computer Science (expected in 2020) \\
Kent State University, Kent, OH, USA. \hspace{0.2in}  GPA 3.82 

\vspace{-0.1in} 

{\sl Bachelor of Science}, Computer Science and Engineering (Jan 2008) \\ % \sl will be bold italic in
					 % New Century Schoolbook (or
					 % any postscript font) and
					 % just slanted in Computer
					 % Modern (default) font
Bangladesh University of Engineering and Technology (BUET), Dhaka, Bangladesh      

\vspace{0.001in} 
\section{\centerline{ PROGRAMMING SKILLS }}
\vspace{2pt}
C; C++; Java; C\#; Python; Shell Script; HTML; CSS; JavaScript 

\vspace{0.001in}
\section{\centerline{ OPEN SOURCE PROJECTS}}
 Linux Kernel, Alladin (an ASIC simulator), Mininet (Network emulator), GStreamer 
\vspace{2pt}
  
\vspace{0.001in} 
\section{\centerline{PROFESSIONAL EXPERIENCE}} 
\vspace{3pt}
{\sl Graduate Assistant, Kent State University}\\
Kent, OH, USA (Sep, 2013 - present)
  
   \begin{itemize} \itemsep -2pt % reduce space between items
  \item Developed a new routing table lookup algorithm and several existing best performing algorithms such as Poptrie and SAIL. Implemented them as a stand-alone application, inside ASIC simulator and inside Linux kernel (in C). Evaluated the algorithms with the routing tables from real core routers.
  \item Implemented power and area calculation in Aladdin (an ASIC simulator) where logic gates are not shared across pipeline stages.
  \item Implemented a router-assisted TCP in Linux kernel where TCP sending rate is calculated based on the explicit feedback from router (in C). The router-assisted TCP performs better than delay-based congestion control (currently used in Google Hangout) for video conferencing.  
  \item Implemented RCP protocol for network processor based routers using Linux eBPF (in C). 
  \item Implemented RCP protocol in a router data plane using Domino (in C).
  \item Developed a GStreamer based video streaming application (in C).
  \item Developed several experimental network topologies using Mininet (Python).	
 \end{itemize}

{\sl Software Development Intern, inConatact} \\
Columbus, OH, USA (May, 2015 - Aug, 2015)
 \begin{itemize} \itemsep -2pt
	\item Implemented a call dispatching mechanism of call centers where incoming calls are assigned to agents based on various criteria and skill metrics of the agents.(C\#)
	\item  Implemented an interval tree to make an call assignment efficient instead of searching all the agents.
  \end{itemize} \vspace{-6pt}

{\sl Software Development Intern, RightRez} \\
Bloomington, IN, USA (May, 2014 - Aug, 2014)
\begin{itemize} \itemsep -2pt
	\item  Implemented a flight search (BFS and A* search) in a graph of 3 million flight routes (C\#)
	\item  Implemented several heuristics that reduced that searching time from 30 minutes to few seconds.
    \item  Integrated Sabre webservice to implement seat map for airlines. (C\#)
\end{itemize} \vspace{-6pt}

{\sl Senior Software Engineer, GenWeb2} \\
Dhaka, Bangladesh (Sep, 2012 - Jul, 2013)
\begin{itemize} \itemsep -2pt
	\item  Implemented a 3D simulator of a CNC machine. (C++, OpenGL, Qt)
	\item  Calculated the minimum number of points to draw an arc based on the arc length. It reduced the CPU and memory consumption by almost 90\%
	\item Developed a backend of a mobile application that is used for charging electric cars. (Java, Postgresql) 
\end{itemize} \vspace{-6pt}
 
{\sl Software Engineer, KB Group} \\
Dhaka, Bangladesh (Apr, 2010 - Sep, 2011)
 \begin{itemize}
 \item  Implemented an end-to-end ticketing system for box offices. (C\#, SQL Server)
  \item  Integrated payment gateways to e-commerce and box office applications. (C++, COM, Classic ASP, SQL Server).
 \end{itemize} 
 
{\sl Software Engineer, Arista Enterprises}  \\
Dhaka, Bangladesh (Apr, 2009 - Mar, 2010)
\begin{itemize} 
\item  Implemented an end-to-end airline ticket booking system (C\#, ASP.NET, SQL Server, HTML, CSS, JavaScript). 
\end{itemize}  

{\sl Software Engineer, SDSL}  \\
Dhaka, Bangladesh (Feb, 2008 - Mar, 2009)
\begin{itemize}
\item Developed a map navigator for feature phones and windows mobile with AfriGIS map. Worked on zooming, panning and caching of map tiles and data. (J2ME, C\#).
\end{itemize} 
 
\vspace{0.01in} 
\section{\centerline{PUBLICATIONS}} 
\vspace{10pt}
\begin{itemize}
   \item \textbf{MD Iftakharul Islam}, Javed I Khan "SAIL Based FIB Lookup in a Programmable Pipeline Based Linux Router." IEEE High Performance Switching and Routing (HPSR), 2019.
   \item \textbf{MD Iftakharul Islam}, Javed I Khan "Leveraging Domino to Implement RCP in a Stateful Programmable Pipeline." IEEE High Performance Switching and Routing (HPSR), 2019.
   \item \textbf{MD Iftakharul Islam}, Javed I Khan "A Network-centric TCP for Interactive Video Delivery Networks (VDN)." IEEE International Conference on Network Protocols (ICNP), 2017.		      
   \item \textbf{MD Iftakharul Islam}, Javed I Khan "Video Splicing Techniques for P2P Video Streaming." IEEE ICDCS workshop on Computer and Networking Experimental Research using Testbeds (CNERT), 2015.
   
\end{itemize}


\vspace{0.01in} 
\section{\centerline{SERVICES}} 

\begin{center}
\begin{itemize}
	\item Reviewer of IEEE Journal of Selected Area of Communication (JSAC).
	\item Reviewer of Computer Networks, Elsevier.	
	\item Shadow reviewer of Network and Computer Applications, Elsevier.
\end{itemize}
 \end{center}


\vspace{0.01in} 
\section{\centerline{Teaching}} 

\begin{center}
	\begin{itemize}
		\item Lab instructor for CS-III (Programming Pattern) from 2017-2020
		\item Lab instructor for CS-I (Procedural and Object-Oriented Programming) from 2016-2017
	\end{itemize} 
\end{center}
 
  
\end{resume} 
\end{document}













