% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\usepackage{hyperref}
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{24pt} % allow room for 2-line header
\setlength{\headsep}{24pt}  % space between header and text
\setlength{\headheight}{24pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
\rhead{ {\it Tamim}\\{\it p. \thepage} } % put text in header (right side)
\cfoot{}                                     % the foot is empty
\topmargin=-0.5in % start text higher on the page

\begin{document}
\thispagestyle{empty} % this page has no header  
\name{MD Iftakharul Islam\\[12pt]}% the \\[12pt] adds a blank line after name

\address{
  Website: \url{https://tamimcse.github.io/}\\
  Email: mislam4@kent.edu
  }      
                                      
\address{
Kent, Ohio, USA \\
Phone: 330-389-3188
  }
\begin{resume}

\section{\centerline{EDUCATION}} 
\vspace{2pt} 
{\sl PhD}, Computer Science (Expected in 2020) \\
Kent State University, Kent, OH, USA. \hspace{0.2in}  GPA 3.82 

\vspace{-0.1in} 

{\sl Bachelor of Science}, Computer Science and Engineering (Jan 2008) \\ % \sl will be bold italic in
					 % New Century Schoolbook (or
					 % any postscript font) and
					 % just slanted in Computer
					 % Modern (default) font
Bangladesh University of Engineering and Technology (BUET), Dhaka, Bangladesh      

\vspace{0.001in} 
\section{\centerline{ PROGRAMMING SKILLS }}
\vspace{2pt}
C; C++; Java; C\#; Python; Shell Script 

\vspace{0.001in}
\section{\centerline{ OPEN SOURCE PROJECTS}}
 Linux Kernel, Alladin (an ASIC simulator), Mininet (Network emulator), GStreamer 
\vspace{2pt}
  
\vspace{0.001in} 
\section{\centerline{PROFESSIONAL EXPERIENCE}} 
\vspace{3pt}
{\sl Kent State University} \hfill        Sep, 2013 - present \\
Kent, OH, USA       \hfill   (Graduate Assistant)
  
   \begin{itemize} \itemsep -2pt % reduce space between items
  \item Developed a new routing table lookup algorithm and several existing best performing algorithms such as Poptrie and SAIL. Implemented them as a stand-alone application, inside ASIC simulator and inside Linux kernel (in C). Evaluated the algorithms with the routing tables from real core routers.
  \item Implemented power and area calculation in Aladdin (an ASIC simulator) where logic gates are not shared across pipeline stages.
  \item Implemented a router-assisted TCP in Linux kernel where TCP sending rate is calculated based on the explicit feedback from router (in C). The router-assisted TCP performs better than delay-based congestion control (currently used in Google Hangout) for video conferencing.  
  \item Implemented RCP protocol for network processor based routers using Linux eBPF (in C). 
  \item Implemented RCP protocol in a router data plane using Domino (in C).
  \item Developed a GStreamer based video streaming application (in C).
  \item Developed several experimental network topologies using Mininet (Python).
  \item     	
 \end{itemize}

{\sl inConatact}       \hfill               May, 2015 - Aug, 2015 \\
Columbus, OH, USA \hfill   (Software Development intern)
 \begin{itemize} \itemsep -2pt
	\item  Simulated a call center where simulated calls are generated based on various probabilistic distributions. The calls are then assigned to
	agents based on their schedule and the skill matrices of the agents have been calculated. (C\#)
	\item  Implemented an interval tree to make the call assignment efficient instead of searching all the agents.
  \end{itemize} \vspace{-6pt}

{\sl RightRez}       \hfill               May, 2014 - Aug, 2014 \\
Bloomington, IN, USA \hfill   (Software Development intern)
\begin{itemize} \itemsep -2pt
	\item  Implemented a BFS and A* search to find flights from a graph consists of 3 million flights (C\#)
	\item  Implemented several heuristics that reduced that searching time from 30 minutes to few seconds.
    \item  Integrated Sabre webservice to implement seat map for airlines. (C\#)
\end{itemize} \vspace{-6pt}

{\sl GenWeb2}       \hfill               Sep, 2012 - Jul, 2013 \\
Dhaka, Bangladesh \hfill   (Senior Software Engineer)
\begin{itemize} \itemsep -2pt
	\item  Implemented a 3D simulator for CNC machines. (C++, OpenGL, Qt) 
	\item  Calculated the minimum number of points to draw an arc based on the arc length. It reduced the CPU and memory usage by almost 90\%
\end{itemize} \vspace{-6pt}
 
{\sl KB Group}       \hfill               Apr, 2010 - Sep, 2011 \\
Dhaka, Bangladesh \hfill   (Software Engineer)
 \begin{itemize}
 \item  Integrated payment gateways to KB Group e-commerce and post office box application. (C++, COM). 
 \item  Implemented a print server that generates PDF tickets and print them by specialized printers (C\#)
 \end{itemize} 
 
{\sl Arista Enterprises} \hfill  Apr, 2009 - Mar, 2010 \\
Dhaka, Bangladesh \hfill   (Software Engineer)
\begin{itemize} 
\item  Implemented end-to-end transaction for an airline booking system (ASP.NET). 
\end{itemize}  

{\sl SDSL} \hfill                  Feb, 2008 - Mar, 2009 \\
Dhaka, Bangladesh \hfill   (Software Engineer)
\begin{itemize}
\item Developed a map client for feature phones for AfriGIS map. Worked on zooming, panning, and caching map tiles. (J2ME). 
\end{itemize} 
 
\vspace{0.01in} 
\section{\centerline{PUBLICATIONS}} 
\vspace{10pt}
\begin{itemize}
   \item \textbf{MD Iftakharul Islam}, Javed I Khan "SAIL Based FIB Lookup in a Programmable Pipeline Based Linux Router." IEEE High Performance Switching and Routing (HPSR), 2019.
   \item \textbf{MD Iftakharul Islam}, Javed I Khan "Leveraging Domino to Implement RCP in a Stateful Programmable Pipeline." IEEE High Performance Switching and Routing (HPSR), 2019.
   \item \textbf{MD Iftakharul Islam}, Javed I Khan "A Network-centric TCP for Interactive Video Delivery Networks (VDN)." IEEE International Conference on Network Protocols (ICNP), 2017.		      
   \item \textbf{MD Iftakharul Islam}, Javed I Khan "Video Splicing Techniques for P2P Video Streaming." IEEE ICDCS workshop on Computer and Networking Experimental Research using Testbeds (CNERT), 2015.
   
\end{itemize}


\vspace{0.01in} 
\section{\centerline{SERVICES}} 

\begin{center}
\begin{itemize}
	\item Reviewer of IEEE Journal of Selected Area of Communication (JSAC).
	\item Reviewer of Computer Networks, Elsevier.	
	\item Shadow reviewer of Network and Computer Applications, Elsevier.
\end{itemize}
 \end{center}
 
 
\end{resume} 
\end{document}













