%!TeX program = pdflatex
% Geoff Boeing's Curriculum Vitae
% Email: boeing@usc.edu
% Web: https://geoffboeing.com/
% Repo: https://github.com/gboeing/cv

\documentclass[11pt,letterpaper]{report}

\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{setspace} % custom line spacing

% what is your name?
\newcommand{\myname}{MD Iftakharul Islam}

% select default typefaces
\usepackage{ebgaramond} % document's serif typeface
\usepackage{tgheros}    % document's sans serif typeface

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\SetTracking{encoding=*, family=\sfdefault}{30} % increase sans serif headings tracking
\titleformat{\section}{\lsstyle\sffamily\small\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{30pt plus 4pt minus 4pt}{8pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\sffamily\footnotesize\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{16pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (assumes letter paper)
\geometry{body={6.5in, 9.0in},
    left=1.0in,
    top=1.0in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{0.9}

% define space between list items
\newcommand{\listitemspace}{0.25em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = black,
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdfkeywords = {city planning, housing, street networks, transportation, urban design, urban informatics},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \raggedright{}

    % display your name as the document title
    \namefont{\myname}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{0.700\textwidth}
        % current primary affiliation, left-aligned
        Staff Engineer, \\
        Samsung Austin Semiconductor,\\
        Samsung Advanced Computing Labs (ACL),\\
        San Jose, CA.
    \end{minipage}
    \begin{minipage}[t]{0.295\textwidth}
        % contact info details, right-aligned
        \flushright{}
        \href{mailto:mislam4@kent.edu}{mislam4@kent.edu} \\
        +1 330 389 3188 \\
        \href{https://tamimcse.github.io/}{https://tamimcse.github.io} \\
        Palo Alto, CA.
    \end{minipage}


    \section*{Education}

    \begin{tablist}

        \item[Ph.D.] \tab{}Computer Science, Kent State University, Kent, OH, USA. (Date received: 08/20/2022)
        \item[B.Sc.]  \tab{}Computer Science and Engineering, BUET, Dhaka, Bangladesh (Date received: 01/06/2008).

    \end{tablist}

    \section*{PhD Dissertation}

An IPv6 Routing Table Lookup Algorithm in Software and ASIC by Designing a High-Level Synthesis System


    \section*{Research Areas}

    \begin{itemize}

        \item CGRA and GPU Compiler and Simulator
        \item High-Level Synthesis compiler
        \item Network Algorithms

    \end{itemize}

    \section*{Technical Skills}

\begin{itemize}
	\item C++ 
	\item C
\end{itemize}


\section*{Work Experience}
\subsection*{Staff Engineer}{Samsung Austin Semiconductor, San Jose, CA}\\{04/03/2023 -- Present}
\begin{itemize}
	\item I worked on GPU functional modeling. I primarily worked on the command processor (CP) block of the GPU. There I worked on integrating RISC-V based core in CP. I also worked on other CP functionalities such as last level cache (LLC) preloading, context versioning and so on. 
\end{itemize}


\subsection*{Software Engineer 3}{Juniper Networks, Sunnyvale, CA}\\{01/10/2022--03/27/2023}
\begin{itemize}
	\item I worked on Packet forwarding software of Juniper Express ASIC. I mainly worked on packet classification algorithms (e.g. prefix match, range match, TCAM match, etc). I also worked on compiler that maps network rules to ASIC.
\end{itemize}


\subsection*{Graduate Assistant}{Kent State University, Kent, OH}\\{Sep 2013-Dec 2022}
\begin{itemize}
	\item Taught Design Patterns and Object Oriented Programming in C++.
\end{itemize}


\subsection*{Software Engineer -- Intern}{inContact, Columbus, OH}\\{May 2015-Aug 2015}
\begin{itemize}
	\item Developed a call center simulation platform (C\#).
\end{itemize}


\subsection*{Software Engineer - Intern}{RightRez, Bloomington, IN}\\{May 2014-Aug 2014}
\begin{itemize}
	\item Developed a flight search algorithm (C\#).
\end{itemize}


\subsection*{Senior Software Engineer}{GenWeb2, Dhaka, Bangladesh}\\{Sep 2012 -- Jul 2013}
\begin{itemize}
	\item Developed a 3D simulator of CNC machines (C++)
\end{itemize}


\subsection*{Software Engineer}{KB Group, Dhaka, Bangladesh}\\{Apr 2010 - Sep 2011}
\begin{itemize}
	\item Developed ticketing systems for theaters (C++).
\end{itemize}


\subsection*{Software Engineer}{Arista Enterprises, Dhaka, Bangladesh}\\{Apr 2009--Mar 2010}
\begin{itemize}
	\item Developed an airline ticket booking system (C\#).
\end{itemize}



\subsection*{Software Engineer}{SDSL, Dhaka, Bangladesh}\\{Feb 2008--Mar 2009}
\begin{itemize}
	\item Developed a map navigator for AfriGIS map (C\#)
\end{itemize}



    \section*{Publications}



    \begin{tablist}
        \item[2021] \tab{}\underline{MD Iftakharul Islam}, Javed I Khan "C2RTL: A High-level Synthesis System for IP Lookup and Packet Classification." \textit{IEEE 22nd International Conference on High Performance Switching and Routing (HPSR)}. Paris, France.\@ \href{https://ieeexplore.ieee.org/document/9481810}{doi:10.1109/HPSR52026.2021.9481810}
    	
        \item[2021] \tab{}\underline{MD Iftakharul Islam}, Javed I Khan "CP-Trie: Cumulative PopCount based Trie for IPv6 Routing Table Lookup in Software and ASIC." \textit{IEEE 22nd International Conference on High Performance Switching and Routing (HPSR)}. Paris, France.\@ \href{https://ieeexplore.ieee.org/document/9481816}{doi:10.1109/HPSR52026.2021.9481816}

        \item[2019] \tab{}\underline{MD Iftakharul Islam}, Javed I Khan "SAIL based FIB lookup in a programmable pipeline based Linux router." \textit{IEEE 20th International Conference on High Performance Switching and Routing (HPSR)}. Xi'an, China.\@ \href{https://ieeexplore.ieee.org/document/8808129}{doi:10.1109/HPSR.2019.8808129}

        \item[2019] \tab{}\underline{MD Iftakharul Islam}, Javed I Khan "Leveraging Domino to implement RCP in a stateful programmable pipeline." \textit{IEEE 20th International Conference on High Performance Switching and Routing (HPSR)}. Xi'an, China.\@ \href{https://ieeexplore.ieee.org/document/8808107}{doi:10.1109/HPSR.2019.8808107}
        
        \item[2017] \tab{}\underline{MD Iftakharul Islam}, Javed I Khan "A network-centric TCP for interactive video delivery networks (VDN)." \textit{IEEE 25th International Conference on Network Protocols (ICNP) Workshop PVE-SDN}. Toronto, ON, Canada.\@ \href{https://ieeexplore.ieee.org/document/8117596}{doi:10.1109/ICNP.2017.8117596}

        \item[2015] \tab{}\underline{MD Iftakharul Islam}, Javed I Khan "Video splicing techniques for P2P video streaming." \textit{IEEE 35th International Conference on Distributed Computing Systems (ICDCS) Workshops}. Columbus, OH, USA.\@ \href{https://ieeexplore.ieee.org/document/7165086}{doi:10.1109/ICDCSW.2015.23}

        \item[2009] \tab{}\underline{MD Iftakharul Islam}, Md Mostofa Akbar "Heuristic algorithm of the multiple-choice multidimensional knapsack problem (MMKP) for cluster computing." \textit{12th International Conference on Computers and Information Technology (ICCIT)}. Dhaka, Bangladesh.\@ \href{https://ieeexplore.ieee.org/document/5407147}{doi:10.1109/ICCIT.2009.5407147}
        
    \end{tablist}




    \section*{Service}


    \subsection*{Academic Journal Peer Review}

	\begin{itemize}
		\item IEEE Transaction on Networking (ToN)
		\item IEEE Journal of Selected Area of Communication (JSAC)
		\item Journal of Parallel and Distributed Computing (JPDC)
	\end{itemize}






    % display today's date as Month Year after a vertical space below the end of the text
    \begin{center}
        \vfill
        Updated \monthyeardate\today
    \end{center}

\end{document}
