\cvsection{TECHNICAL SKILLS}
\cvtag{C}
\cvtag{Router Architecture}
\cvtag{High Level Synthesis}
\cvtag{Linux Kernel}
\cvtag{C++}
\cvtag{Java}
\cvtag{C\#}
\cvtag{Python}
\cvtag{Verilog}
\cvtag{HTML/CSS}
\cvtag{JavaScript}\\
%\divider
% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{Projects}
\cvproject{Genetic Algorithm for Code Golf Music}
\begin{itemize}
\item Synthesizing Music Information Retrieval (MIR) and genetic algorithms to discover and improve short, music generating lines of C code.
\item Implementing the model using a similar approach to the Ramanujan Machine.
\end{itemize}
\smallskip
\cvproject{HealthHub}
\begin{itemize}
\item Designing and developing an electronic health records system focusing on aiding and assisting patients as well as providing a smoother data management experience for healthcare personnel (e.g. Physicians, Nurses, etc.).
\end{itemize}
\smallskip
\cvproject{Pitch Detection and Synthesis}
\begin{itemize}
\item Developed an MIR algorithm to detect pitches in .mp3 files, reproduce them in MIDI, and synthesize them using custom wave formats.
\item Used real-time signal processing to visualize the outputs generated by the algorithm.
\end{itemize}
\smallskip
\cvproject{Booking Website}
\begin{itemize}
\item Designed and developed a flight booking website from scratch, providing multiple services to both end-consumers and airlines.
\item Implemented the website using Python, Flask, SQL, JS and HTML/Bootstrap/CSS.
\end{itemize}
\smallskip
\cvproject{Automated Performance Reporting System}
\begin{itemize}
\item Solely developed a program to automatically generate quarterly performance reports for Arch Global Advisors, scraping the web to get historical stock price data, dividend data, and earnings release dates.
\item Ultimately cut the firm's reporting process from days to minutes.
\end{itemize}

\cvsection{Publications}
\begin{itemize}
   \item \underline{MD Iftakharul Islam}, Javed I Khan "SAIL Based FIB Lookup in a Programmable Pipeline Based Linux Router." IEEE HPSR, 2019.
\item \underline{MD Iftakharul Islam}, Javed I Khan "Leveraging Domino to Implement RCP in a Stateful Programmable Pipeline." IEEE HPSR, 2019.
\item \underline{MD Iftakharul Islam}, Javed I Khan "A Network-centric TCP for Interactive Video Delivery Networks (VDN)." IEEE ICNP Workshop PVE-SDN, 2017.

\end{itemize}

\cvproject{}